Experiment 2 of 4

### 2016-10-01 experiments/e2/writeup/e2-analysis-extra-stuff.Rmd
umm

#Lmer model: before outlier removal

>>>>

```{r e2-rtplot, fig.width=7, fig.height=3.5, echo=FALSE, message=FALSE, dev='pdf'}
dd$RT_log=log(dd$RT)
rtdata=dd
source('summarySEwithin2.R')
rtdataplot1 <- summarySEwithin2(rtdata, measurevar="RT_log", 
                                withinvars=c("Vagueness", "Number", "Item"), idvar="Subject")
rtdataplot1$Condition <- as.factor(paste(sep=':', rtdataplot1$Number, rtdataplot1$Vagueness))
rtplot=ggplot(rtdataplot1, aes(y=RT_logNormed, x=Item, group=Condition, fill=Vagueness)) +
  geom_line() +
  geom_errorbar(width=.2, aes(ymin=RT_log-ci, ymax=RT_log+ci)) +
  geom_point(size=2, col=1, aes(shape=Vagueness)) +
  scale_fill_grey(name="Vagueness", start=0, end=1) +
  scale_shape_manual(name="Vagueness", values=c(21,22)) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab(NULL) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), legend.position="top",
        aspect.ratio=1,
        plot.background=element_rect(fill=NA, color='white'),
        strip.background=element_blank(),
        axis.text.x = element_text(angle = 15)) +
  facet_grid(~Number)
rtplot
```
#Lmer model: before outlier removal
